Model based reinforcement learning at FERMI FEL

### 2020-11-16 main.tex
txs auto checkin

\begin{figure}[!h]
	\centering
	\includegraphics*[width=0.5\textwidth]{Figures/MBRL_overview}
	\caption{A schematic overview of the AE-Dyna approach used in this paper.}
	\label{fig:MBRL_overview}
\end{figure}
\subsection{Critical design decisions}
In the following the most important aspects of a successful application of a Dyna-AE algorithm are listed:
\begin{itemize}
	\item The ANN - including the prior - number of models - noise level.
	\item The number of data points and the policy.
	\item The uncertainty - how is this included?
	\item The episodic design - avoid long trajectories.
	\item The MFRL agent as e.g. the TRPO and PPO or the SAC.
\end{itemize}
We try to discuss all items in some detail in the following.
The anchoring ensemble methods usually yields good results already with a small number of different networks. The idea behind it, is to mimic the posterior probability of the dynamics model to capture first of all its own uncertainty due to the lack of data. Empirical results show that three to five models were sufficient to see clear advantages over a single network approach and the main goal is not to calculate the exact posterior of the model. A small two-layer network with around 15-25 nodes and the $tanh$ activation were used. The last layer was linear and the inputs were normalized to the interval [-1,1]. 
\subsection{Operational deployment}
\NB{Niky} % come abbiamo interagito con FERMI
\subsection{\NB{short FERMI introduction}}
The Free Electron laser Radiation for Multidisciplinary Investigation  better known as the FERMI, is the seeded free-electron laser facility next to the third-generation synchrotron facility ELETTRA at the Elettra Sinchrotrone Trieste laboratories.
A free-electron laser is a fourth-generation light source where the lasing medium consists of very-high-speed electron moving freely through a magnetic structure. The FERMI peculiarity is given by the usage of an external seeding source that provides several advantages, as the increased stability in pulse and photon energy, reduced size of the device, improved longitudinal coherence, more control on the pulse structure, and improved temporal synchronization with external timing systems.

>>>>

\begin{figure}[!h]
	\centering
	\includegraphics*[width=0.5\textwidth]{Figures/MBRL_overview}
	\caption{A schematic overview of the AE-Dyna approach used in this paper.}
	\label{fig:MBRL_overview}
\end{figure}
\subsection{Critical design decisions}
In the following the most important aspects of a successful application of a Dyna-AE algorithm are listed:
\begin{itemize}
	\item The ANN - including the prior - number of models - noise level.
	\item The number of data points and the policy.
	\item The uncertainty - how is this included?
	\item The episodic design - avoid long trajectories.
	\item The MFRL agent as e.g. the TRPO and PPO or the SAC.
\end{itemize}
We try to discuss all items in some detail in the following.
The anchoring ensemble methods usually yields good results already with a small number of different networks. The idea behind it, is to mimic the posterior probability of the dynamics model to capture first of all its own uncertainty due to the lack of data. Empirical results show that three to five models were sufficient to see clear advantages over a single network approach and the main goal is not to calculate the exact posterior of the model. A small two-layer network with around 15-25 nodes and the $tanh$ activation were used. The last layer was linear and the inputs were normalized to the interval [-1,1]. The prior is controlled by the initialization of the weights, which were normalized by the number of nodes in each layer. The noise level is also respected during the initialization. For the moment only homeoscetastic errors are used.\\
One of the most crucial points is how this uncertainties are taken into account by the RL algorithms. Several different approaches were tried. It is possible to take the average of the models and add Gaussian noise leveled by the standard deviation of the models. Another straight forward way is to randomly select a model to provide the next step.

\subsection{Operational deployment}
\NB{Niky} % come abbiamo interagito con FERMI
\subsection{\NB{short FERMI introduction}}
The Free Electron laser Radiation for Multidisciplinary Investigation  better known as the FERMI, is the seeded free-electron laser facility next to the third-generation synchrotron facility ELETTRA at the Elettra Sinchrotrone Trieste laboratories.
A free-electron laser is a fourth-generation light source where the lasing medium consists of very-high-speed electron moving freely through a magnetic structure. The FERMI peculiarity is given by the usage of an external seeding source that provides several advantages, as the increased stability in pulse and photon energy, reduced size of the device, improved longitudinal coherence, more control on the pulse structure, and improved temporal synchronization with external timing systems.
